### 2021-07-09 paper/paper.tex
once through with final edits

We would like to think that our unit tests of code match perceived risk, that they match the components by which we judge risk: the hazard for failure, the cost of mitigating failure, and how much a result matters. However, user studies of the behavior of test authors show that our choices about testing are ruled by what is convenient within a given testing framework~\cite{Wiklund2017-ms}.

@@

\vskip 6pt
There are two circumstances where this is crucial. The first is that you have to test a slow function, such as a large, Monte Carlo inference. If the function under test runs for hours or days, then selective testing can respect resource limitations.

\vskip 6pt
The other circumstance is when there is a large test space. We've been talking about a function under test, but this is a stand-in for any test we can parametrize. Let's say we've written an application, that we've unit tested its important supporting functions, and we want to write user-level tests that look for problems from interactions among command-line arguments and choices in parameter files. This can be equivalent to testing a function with twenty or more arguments. Twenty arguments, with four possible values each, would lead to over $10^{12}$ ways to call this function.

@@

\section{How to Use Combinatorial Testing}\label{sec:how-to-use}

@@

While you may already know how to use \cit from the snippet in the introduction, it can help to think of automated test case generation as a set of steps, each of which has choices to make.
\begin{enumerate}
   \item Identify the system under test.
   \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
   \item Address the risk associated with different arguments.
   \item Pick a test generation strategy.
   \item Choose a method for checking the results of each test.
\end{enumerate}
We'll explore these steps in this section.

@@

\subsubsection{What arguments represent}
There are two choices to make about arguments and their values. We must decide what the arguments represent and must select particular values for those arguments.

\vskip 6pt
It's rare that a function expects arguments that really take only a few possible values. We use integers, floating-point, and strings, but a function argument can be any struct. When we specify tests for \cit, and we choose a few argument values, they are representatives of equivalence classes.

\vskip 6pt
An \emph{equivalence class} is a set of input values that would discover the same faults in the code. For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults. As authors of unit tests, we select argument values that represent equivalence classes for the function under test. You can choose them by looking at the code or by looking at a specification for the function, but it's possible to miss an equivalence class and miss the faults discovered by that equivalence class.

@@

\vskip 6pt
There are other creative ways to apply automatic test case generation. For instance, if an application reads a \csv file, we can use \cit to ensure rows of that \csv have a wide mixture of column values. This would improve branch coverage in code that reads the \csv as a data frame. Similarly, for module-level testing, arguments could represent choices about calls to a module's functions. Here, consecutive arguments become function calls that are consecutive in time.

@@

Sometimes combinations of function arguments don't make sense. Imagine we have a function with two arguments.
\begin{lstlisting}[language=Julia]
arg1 = ["quick", "complicated"]
arg2 = [0.0, 1.0, 10.0]
\end{lstlisting}
For this example, if the first argument is \verb|"quick"|, then the second argument must be \verb|0.0|. If we generate all combinations of \verb|arg1| and \verb|arg2|, then some combinations won't make sense. The domain of the function isn't merely the sum of the domains of the arguments.

\vskip 6pt
One way to solve this problem is to rewrite the argument list to have a single argument that reflects only the allowed combinations. This replaces \verb|arg1| and \verb|arg2|.
\begin{lstlisting}[language=Julia]
arg12 = [("quick", 0.0), ("complicated", 0.0),
    ("complicated", 1.0), ("complicated", 10.0)]
\end{lstlisting}
It can be more convenient to tell the \cit algorithm that certain combinations are forbidden~\cite{Petke2015-ex,Grindal2006-vy}.
\begin{lstlisting}[language=Julia]
forbid(arg1, arg2) = arg1 == "quick" && arg2 > 0.0
test_set = full_factorial(
    arg1, arg2; disallow = forbid)
\end{lstlisting}
For testing functions with many arguments, this is simpler to use.

\vskip 6pt
Sometimes we want to begin with tests that are particular happy paths. These might be statistically common call signatures, or they could be pre-specified in design documents. Given that our goal is to minimize resource usage, we should ensure that any tuples of argument values covered in these initial calls are included in our list of covered tuples.
\begin{lstlisting}[language=Julia]
must_test = [[1, "mid", 3.7, :relax],
             [1, "mid", 4.9, :relax]]
test_cases = all_pairs(
    [1, 2, 3], ["low", "mid" ,"high"],
    [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
    seeds = must_test
    )
\end{lstlisting}
They are called seed cases and are specified with an explicit option in \utd.

@@

The combinatorial testing approach gives you a lever with which to address perceived risk in code. You decide the wayness of coverage, which is the number of arguments for which all combinations of argument values must appear. As shown in Tab.~\ref{tab:samplecounts}, increasing wayness increases the number of test cases. Pairwise testing has two-way coverage, but higher wayness can yield some benefit~\cite{Petke2015-ex}. Literature on how to generate these tests uses the word coverage to mean two-way, three-way, and so on. The term test coverage usually refers to which lines of code executed (line coverage), if--then decision tests (decision coverage), or branches that are executed during a test (branch coverage).

\vskip 6pt
The two uses of the word coverage are related, because combinations with higher wayness as inputs are designed to lead to more decision coverage of code during execution. There isn't enough evidence for this connection for us to choose wayness according to code's cyclomatic complexity, and we are counseled against making coverage the goal of unit testing~\cite{Inozemtseva2014-gz}.

\vskip 6pt
For \cit, we address risk by ensuring more test cases include new combinations of arguments that affect the control flow of risky code. The first way to increase testing of an argument is to increase the number of values for an argument by adding corner cases. The second way is to increase the wayness of a set of arguments.

@@

\begin{lstlisting}[language=Julia]
array_of_forty_parameters = fill(1:4, 40)
test_set = all_pairs(
    array_of_forty_parameters...;
    wayness = Dict(3 => [[3:6], [25:30]])
    )
\end{lstlisting}
Here, the third through sixth arguments will be tested with a wayness of three, as will the twenty-fifth through thirtieth. It's unclear whether mixing wayness will still yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.

@@

\vskip 6pt
The \emph{excursion} method makes a first test case using the first provided value for each argument. Then, for one-way excursions, it walks the first argument through all values, keeping the rest of the arguments the same. Then it walks the second argument through all values, keeping the rest of the arguments the same, and so on. It asks how the function under test would perform if you were to change any single argument value. A two-way excursion tries changes to any two argument values in combination. It produces considerably more test cases than an all-pairs design.

@@

\vskip 6pt
One solution is to create a parallel implementation of the function under test. It could be an earlier version of the function, using a na{\"i}ve algorithm. It could be a function that computes the same values using a different mathematical representation, such as using numerical integration instead of using the result of symbolic integration. It could be an external implementation, in another language.

@@

There are two ways to improve upon current use of combinatorial test generation. One is to help the tester whose testing resources are limited, by generating fewer test cases that still meet the wayness guarantee. The other is to make it more convenient to use combinatorial testing within the unit testing framework. Here, we could generate tests with so little time and memory that there is no need to cache test cases. Both of these improvements are limited by our need for algorithms that support the features, described in Sec.~\ref{sec:how-to-use}, that make automated test case generation practical to use.

\vskip 6pt
The \utd package expands on the implementation of two $t$-way combinatorial interaction testing algorithms. One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}. The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}. Thile these algorithms have different structure, we were able to add features to them using similar basic moves.

@@

\vskip 6pt
Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation. The most important strategy for designing these algorithms is to generate an ensemble of algorithms and test them against sample inputs.

@@

\vskip 6pt
Random testing also generates test cases, and we know, from Arcuri et al, that these test cases increase code coverage with increasing numbers of test cases, in a predictable way~\cite{Arcuri2012-az}. Random testing also has the benefit that you can run it for an arbitrarily long time during acceptance testing. There is also no requirement that values be completely random within the domain of arguments. They are almost always biased towards values that carry risk, such as empty strings or other corner cases. Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or the ease of specifying sample argument values instead of the complete domain of the arguments.

\vskip 6pt
There are also more mathematical test generation methods, such as orthogonal arrays or Sobol sequences~\cite{He2013-th}. These give an even distribution of values within high-dimensional spaces. They would be excellent to, for instance, seed an optimization problem with local minima, but they aren't designed to explore the space of execution paths of code, in the way that combinatorial methods are.

@@

\vskip 6pt
Property-based testing, for instance, offers a specification to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite. Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails. This is extraordinarily useful for fault-finding but, again, will use more testing resources~\cite{loscher2018automating}.

@@

\section{Conclusion}
Combinatorial interaction testing is an advanced technique because it's tailored to a difficult situation, when you can't afford not to spend the time to make your best guess at test cases. However, this kind of automation is easy to specify and run in Julia's ecosystem. The most difficult part of the transition is shifting from manual checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}.

\vskip 6pt
A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation. They point to the broad applicability of automation for testing and the effectiveness of tools that offer control to the test author.

>>>>

We would like to think that our unit tests of code match how much risk we perceived in that code, that they match the components by which we judge risk: the hazard for failure, the cost of mitigating failure, and how much a result matters. However, user studies of the behavior of test authors show that our choices about testing are ruled by what is convenient within a given testing framework~\cite{Wiklund2017-ms}.

@@

\vskip 6pt
There are two circumstances where this is crucial. The first is that you have to test a slow function, such as a large, Monte Carlo inference. If the function under test runs for hours or days, then selective testing can conserve limited resources.

\vskip 6pt
The other circumstance is when there is a large test space. We've been talking about a function under test, but this is a stand-in for any test we can parameterize. Let's say we've written an application, that we've unit tested its important supporting functions, and we want to write user-level tests that look for problems from interactions among command-line arguments and choices in parameter files. This can be equivalent to testing a function with twenty or more arguments. Twenty arguments, with four possible values each, would lead to over 10\textsuperscript{12} ways to call this function.

@@

\section{How to Use Combinatorial Interaction Testing}\label{sec:how-to-use}

@@

While you may already know how to use \cit from the snippet in the introduction, it can help to think of combinatorial interaction testing as a set of steps, each of which has choices to make.
\begin{enumerate}
   \item Identify the system under test.
   \item Decide how a single test case, consisting of argument values, should correspond to a unit test.
   \item Address the risk associated with different arguments.
   \item Pick a test generation strategy.
   \item Choose a method for checking the results of each test.
\end{enumerate}
We'll explore these steps in this section.

@@

\subsubsection{What arguments represent}
We must decide what the arguments represent and must select particular values for those arguments.

\vskip 6pt
It's rare that a function expects arguments that really take only a few possible values. We use integers, floating-point, and strings, and a function argument can be any struct. When we specify tests for \cit, and we choose a few argument values, they are representatives of equivalence classes.

\vskip 6pt
An \emph{equivalence class} is a set of input values that would discover the same faults in the code. For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults. You can choose them by looking at the code or by looking at a specification for the function, but it's possible to miss an equivalence class and miss the faults discovered by that equivalence class.

@@

\vskip 6pt
There are other creative ways to apply \cit. For instance, if an application reads a \csv file, we can use \cit to ensure rows of that \csv have a wide mixture of column values. This would improve branch coverage in code that reads the \csv as a data frame. Similarly, for module-level testing, arguments could represent choices about calls to a module's functions. Here, consecutive arguments become function calls that are consecutive in time.

@@

Sometimes combinations of function arguments don't make sense. Imagine we have a function with two arguments.
\begin{lstlisting}[language=Julia]
arg1 = ["quick", "complicated"]
arg2 = [0.0, 1.0, 10.0]
\end{lstlisting}
For this example, if the first argument is \verb|"quick"|, imagine that the function under test requires the second argument to be \verb|0.0|. If we generate all combinations of \verb|arg1| and \verb|arg2|, then some combinations won't make sense. The domain of the function isn't merely the sum of the domains of the arguments.

\vskip 6pt
One way to solve this problem is to rewrite the argument list to have a single argument that reflects only the allowed combinations. This replaces \verb|arg1| and \verb|arg2|.
\begin{lstlisting}[language=Julia]
arg12 = [("quick", 0.0), ("complicated", 0.0),
    ("complicated", 1.0), ("complicated", 10.0)]
\end{lstlisting}
It can be more convenient to tell the \cit algorithm that certain combinations are forbidden~\cite{Petke2015-ex,Grindal2006-vy}. Here, the \verb|forbid| function returns \verb|true| when argument values aren't allowed by the function under test.
\begin{lstlisting}[language=Julia]
forbid(arg1, arg2) = arg1 == "quick" && arg2 > 0.0
test_set = full_factorial(
    arg1, arg2; disallow = forbid)
\end{lstlisting}
For testing functions with many arguments, this is simpler to use than rewriting the argument list.

\vskip 6pt
Sometimes we want to begin with tests that are particular happy paths. These might be statistically common call signatures, or they could be pre-specified in design documents as calls that must be tested. Given that our goal is to minimize resource usage, we should ensure that any tuples of argument values covered in these initial calls are included in our list of covered tuples.
\begin{lstlisting}[language=Julia]
must_test = [[1, "mid", 3.7, :relax],
             [1, "mid", 4.9, :relax]]
test_cases = all_pairs(
    [1, 2, 3], ["low", "mid" ,"high"],
    [1.0, 3.7, 4.9], [:greedy, :relax, :optim];
    seeds = must_test
    )
\end{lstlisting}
They are called seed cases and are specified with an explicit option in \utd.

@@

The combinatorial testing approach gives you a lever with which to address perceived risk in code. You decide the wayness of coverage, which is the number of arguments for which all combinations of argument values must appear. As shown in Table~\ref{tab:samplecounts}, increasing wayness increases the number of test cases. Pairwise testing has two-way coverage, but higher wayness can yield some benefit~\cite{Petke2015-ex}. Literature on how to generate these tests uses the word coverage to mean two-way, three-way, and so on. The term test coverage usually refers to which lines of code executed (line coverage), if--then decision tests (decision coverage), or branches that are executed during a test (branch coverage).

\vskip 6pt
The two uses of the word coverage are related, because combinations with higher wayness as inputs are designed to lead to more decision coverage of code during execution. There isn't enough evidence for this connection for us to choose wayness according to code's cyclomatic complexity, and we are counseled against making coverage the goal of unit testing~\cite{Inozemtseva2014-gz}. That leaves the test author to testing as much as you can afford but shifting those tests towards exercising code that is more complex.

\vskip 6pt
For \cit, that means shifting test cases towards combinations of those arguments that affect the control flow of risky code. The first way to increase testing of an argument is to increase the number of values for an argument by adding corner cases. The second way is to increase the wayness of a set of arguments.

@@

\begin{lstlisting}[language=Julia]
array_of_forty_parameters = fill(1:4, 40)
test_set = all_pairs(
    array_of_forty_parameters...;
    wayness = Dict(3 => [[3,4,5,6]])
    )
\end{lstlisting}
Here, the third through sixth arguments will be tested with a wayness of three, generating a total of 64~test cases. It's unclear whether mixing wayness will still yield a small set of test cases because mixed-level covering arrays don't have well-understood bounds~\cite{Cohen2003-pg}, however sample runs show it does produce fewer test cases than raising coverage on all arguments.

@@

\vskip 6pt
The \emph{excursion} method makes a first test case using the first provided value for each argument. Then, for one-way excursions, it walks the first argument through all values, keeping the rest of the arguments the same. Then it walks the second argument through all values, keeping the rest of the arguments the same, and so on. It asks how the function under test would perform if you were to change any single argument value. A two-way excursion tries changes to any two argument values in combination. It produces considerably more test cases than an all-pairs design, as shown in Table~\ref{tab:samplecounts}.

@@

\vskip 6pt
One solution is to create a parallel implementation of the function under test. It could be an earlier version of the function using a na{\"i}ve algorithm. It could be a function that computes the same values using a different mathematical representation, such as using numerical integration instead of using the result of symbolic integration. It could be an external implementation, in another language.

@@

The \utd package expands on the implementation of two $t$-way combinatorial interaction testing algorithms. One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}. The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}. While these algorithms have different structure, we were able to add features to them using similar basic moves.

@@

\vskip 6pt
Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation. We found that a successful strategy for designing these algorithms is to generate an ensemble of variants and test them against sample inputs.

@@

\vskip 6pt
Random testing also generates test cases, and we know, from Arcuri et~al, that these test cases increase code coverage with increasing numbers of test cases in a predictable way~\cite{Arcuri2012-az}. Random testing has the benefit that you can run it for an arbitrarily long time during acceptance testing. There is also no requirement that values be completely random within the domain of arguments. They are almost always biased towards values that carry risk, such as empty strings or other corner cases. Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or from the ease of specifying sample argument values instead of the complete domain of the arguments.

\vskip 6pt
There are also more mathematical test generation methods, such as orthogonal arrays or Sobol sequences~\cite{He2013-th}. These give an even distribution of values within high-dimensional spaces. They would be excellent to, for instance, seed an optimization problem with local minima, but they aren't designed to explore the space of execution paths of code in the way that \cit is.

@@

\vskip 6pt
Property-based testing, for instance, offers a specification to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite. Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails. This is extraordinarily useful for fault-finding but, again, will use more testing resources than \cit in the absence of failures~\cite{loscher2018automating}.

@@

\section{Conclusion}
Combinatorial interaction testing is an advanced technique because it's tailored to a difficult situation, when you can't afford not to spend the time to make your best guess at test cases. However, this kind of automation is easy to specify and run in Julia's ecosystem. The most difficult part of the transition to automated test case generation is shifting from manually-computed checks of test results to checks that work for any combination of arguments, as described in Sec.~\ref{sec:results}. A lot of the strategies in Sec.~\ref{sec:how-to-use} apply to any kind of automated test case generation. They point to the broad applicability of automation for testing and the effectiveness of tools that offer control to the test author.
